---
title: "HW2"
output: html_document
date: "2022-10-04"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidymodels)
library(tidyverse)
abalone <- read_csv("abalone.csv")
```

1. Predict abalone age
```{r}
abalone$age <- abalone$rings + 1.5
plot(abalone$age)
```
Assess and describe the distribution of age.
  Majority of their ages seem to be between 8 to 13.

2. 
```{r}
set.seed(1738)

abalone_split <- initial_split(abalone, prop = 0.7, strata = age)
abalone_train <- training(abalone_split)
abalone_test <- testing(abalone_split)
```


3. Create a recipe predicting the outcome variable, age, with all other predictor variables.
Explain why you shouldn’t use rings to predict age.
```{r}
abalone_recipe <- recipe(age ~ type + longest_shell + diameter + height + whole_weight + shucked_weight + viscera_weight + shell_weight, data = abalone_train) %>%
  step_dummy(all_nominal_predictors()) %>%
  step_interact(~starts_with("type"):shucked_weight) %>%
  step_interact(~longest_shell:diameter) %>%
  step_interact(~shucked_weight:shell_weight) %>%
  step_center(longest_shell, diameter, height, whole_weight, shucked_weight, viscera_weight, shell_weight) %>%
  step_scale(longest_shell, diameter, height, whole_weight, shucked_weight, viscera_weight, shell_weight)

abalone_recipe
```
Rings are directly correlated with age, so we can't use rings to predict age. 

4. Create and store a linear regression object using the "lm" engine.
```{r}
lm_model <- linear_reg() %>%
  set_engine("lm")
```


5. Workflow set up
```{r}
lm_wkflow <- workflow() %>%
  add_model(lm_model) %>%
  add_recipe(abalone_recipe)
lm_wkflow
```


6. Use your fit() object to predict the age of a hypothetical female abalone with longest_shell = 0.50, diameter = 0.10, height = 0.30, whole_weight = 4, shucked_weight = 1, viscera_weight = 2, shell_weight = 1.
```{r}
lm_fit <- fit(lm_wkflow, abalone_train)
lm_fit %>%
  extract_fit_parsnip() %>%
  tidy()

new_obs <- tibble(
  longest_shell = c(0.5), diameter = c(0.10), height = c(0.30), whole_weight = c(4), shucked_weight = c(1), viscera_weight = c(2), shell_weight = c(1), type = c('F')
  )
new_pred <- new_obs %>%
  bind_cols(lm_fit %>%
              predict(new_data = new_obs))
new_pred

```
Predicted Age: 21.94

7. 
```{r}
library(yardstick)
new_metric <- metric_set(rsq, rmse, mae)
preds <- abalone_train %>%
  select(age) %>%
  bind_cols(lm_fit %>%
              predict(abalone_train))
preds %>%
  new_metric(age, .pred)
```
R^2: 0.55
Root Mean Square Error: 2.16
Mean Absolute Error: 1.55

R^2 depicts how well the predicted values fit the actual values. Since ours is about 0.55, that means about 55% of the observed variabilty is explained by our model. 